
\section{Experience}

\outerlist{

\entrybig
	{\textbf{Fitchburg State University}}{Fitchburg, MA}
	{Peer Tutor at the Tutor Center and Expanding Horizons Office}{September 2017 to May 2020}
\innerlist{
	\entry{CRLA certified tutor.}
	\entry{Tutored students in many different mathematics courses ranging from precalculus, multivariate calculus, statistics, and linear algebra in a walk-in setting.}
	\entry{Also tutored Economics courses including introductory Macroeconomics and Microeconomics.}
	\entry{Effectively communicated different mathematical subjects to multiple students at the same time.}
	\entry{Great interpersonal skills.}
	\entry{Also tutored in a remote setting due to the COVID-19 pandemic.}
}

\entrybig
	{\textbf{Fitchburg State University}}{Fitchburg, MA}
	{Peer Tutor for Summer Bridge Program}{Summer 2018 and 2019}
\innerlist{
	\entry{Tutored students taking a basic mathematics course in a classroom setting.}
	\entry{Adapted to many different mathematical problem types.}
	\entry{Worked under pressure due to high student to faculty ratio.}
}

\entrybig
	{\textbf{Fitchburg State University}}{Fitchburg, MA}
	{Health of the Nashua River: Mathematical Modeling Student Researcher}{Summer 2019}
\innerlist{
	\entry{Used a spatial model to predict locations of contaminants in the Nashua River Watershed using GIS data. }
	\entry{Collaborated with faculty and students of the program to create effective models.}
	\entry{Presented a clear and concise summary of findings.}
	
}

}
